\begin{center}\rule{3in}{0.4pt}\end{center}

\section{Ashok Manda}

\begin{center}\rule{3in}{0.4pt}\end{center}

\subsection{About Me}

I am Senior Software Engineer highly effective at developing new
programs and fixing problems with existing systems. Proficient in
javascript, Agile/Scrum methodology and good in problem solving. Mostly
work on JavaScript Programming language with NodeJs, AngularJs
framework.

\subsection{Skills}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  C/C++
\item
  NodeJs
\item
  AngularJs
\item
  MySQL
\item
  Couchbase
\item
  JavaScript
\item
  PHP(Laravel)
\item
  Redis
\item
  Socket.io
\item
  Elastic Search
\end{itemize}

\subsection{Competitive Programming}

\subsubsection{\href{http://en.wikipedia.org/wiki/Competitive_programming\#Online_contest_and_training_resources}{Profiles}}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  \href{http://codechef.com}{CodeChef} :
  \href{http://codechef.com/users/ashokchoudhary}{ashokchoudhary}
\item
  \href{https://www.hackerearth.com}{Hackerearth} :
  \href{https://www.hackerearth.com/@ashokmanda32}{ashokmanda32}
\item
  \href{http://hackerrank.com}{HackerRank} :
  \href{https://www.hackerrank.com/codelove}{codelove}
\end{itemize}

\subsection{Education}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Bachelor of Technology : Information Technology at \textbf{National
  Institute Of Technology - Kurukshetra, Haryana}
\end{itemize}

\subsection{Contact Me}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Gmail : \href{mailto:ashokmanda32@gmail.com}{ashokmanda32@gmail.com}
\item
  GitHub : \href{http://github.com/ask664}{ask664}
\item
  Twitter : \href{http://twitter.com/askm664}{askm664}
\item
  LinkedIn :
  \href{https://www.linkedin.com/in/ashok-manda-64a33aa2/}{Ashok Manda}
\end{itemize}

\subsection{Work History}

\subsubsection{Senior Software Engineer at Colortokens India LLP,
Bangalore, Karnataka}

\subparagraph{2019-05 - Current}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Develop backend and frontend of application instrumentation user
  events dashboard. Tech Stack - NodeJs, AngularJS, JavaScript,
  Couchbase
\item
  Optimized database query for speed and performance of couchbase
  database with ottomon ORM model
\item
  Worked on code coverage and integration testing for detect, rectify
  such errors and code improvement of application using mocha and
  nyc(istanbul).
\item
  Designed and developed database schema and analytical data structures.
\item
  Worked on PHP agent installation with OPENRASP and Data-dog for
  monitoring application service for generating events.
\end{itemize}

\subsubsection{Software Engineer at Tagtaste Food Pvt Ltd, New Delhi,
Delhi}

\subparagraph{2017-04 - 2019-05}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Make a whole chat system on platform and notification system using
  socket.io, redis and php(laravel) to node using pub-sub.
\item
  Managed all backend RESTful API and devops.
\item
  Used API gateway and make micro services using lambda function for
  event-driven serverless service.
\item
  Designed and developed Database architecture and schema.
\item
  Implemented new tech like database redis and improvement search engine
  using elastic search.
\end{itemize}

\subsubsection{Full Stack Developer at Jugnoo, Chandigarh, Chandigarh}

\subparagraph{2016-06 - 2017-04}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Worked on live tracking of driver and user in web using socket.io from
  client side.
\item
  Worked in analytics team as backend developer using nodejs, mySql.
\item
  Implemented rest API internal support panel and admin panel.
\item
  Worked on internal panel as frontend technology angularJs
\end{itemize}

\subsubsection{Internship at Mebelkart Pvt Ltd, Bangalore,, Karnataka}

\subparagraph{2015-05 - 2015-07}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Worked on ideabook or wishlist of ecommerce website using PHP
  codeignitor framework.
\end{itemize}

Others

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Contribution on OPENRASP PHP project for error fixing.
\item
  Contribution on ottomon couchbase ORM package for optimize N1ql query.
\item
  Worked on Search Engine using mongoDB using college students and
  teachers data and create internal panel.
\end{itemize}

\subsection{Honors}

\begin{itemize}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Committee Head of Technobyte college technical society.
\item
  Won Web Hunt Contest in Techsparadha(national level technical fest).
\end{itemize}